DeloreanJS: Un Debugger en el Tiempo para JavaScript

### 2019-03-20 paper/main.tex
segunda version del paper

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=.7\linewidth]{fig-kont}
\caption{The flowchart of Listing~\ref{lst:rhino_1}, which uses the continuation
  \co{kont}. The invocation of \co{kont} uses a \co{parameter} to replace the
  return value of the anonymous function inside of \co{add} (\ie ``\co{return 1}'').}
\label{fig:kont}
\end{center}
\end{figure*}

This section briefly introduces \callcc and then explains how \synccc uses
them. Programming languages like Scheme provide continuations~\cite{fw84}, which
capture and store the current program control state as a first-class value. If
this value is a function, it can be called and the current continuation will be
replaced with the stored continuation. \unwinder~\cite{unwinder:2018} is a
\javascript library that captures the current continuation with a built-in
function, named \co{callCC}. We illustrate \callcc in \unwinder through a piece
of code that captures the execution of a function adding two numbers
(Listing~\ref{lst:rhino_1}):

%\break

\begin{lstlisting}[linewidth=\columnwidth,numbers=left,caption=Use of continuations in the \unwinder library., label=lst:rhino_1]
var kont;

function add(x,y) {
  return x + (function() {
                kont = callCC(cont => cont);
                return typeof(kont) == "number"? kont:y;})();
}

show(add(5,1));                           //show 6
if (typeof(kont) == "function") kont(20); //show 25
\end{lstlisting}

Figure~\ref{fig:kont} shows a flowchart of the piece of code above. In Line~5,
the piece of code captures and stores the continuation in \co{kont} before
adding \co{y}. This capture takes place in Line~9 when \co{add} is called.  The
result of \co{add} is passed to \co{show}, and then the number \co{6} is
displayed.  Line~10 executes the continuation bound to \co{kont} with \co{20} as
parameter, which replaces the return of the anonymous function of Line~6 (\ie
\co{return 1} $\rightarrow$ \co{return 20}). As a result, \co{25} is displayed
(\co{25 = (x = 5) + (y = 20)}). Note that the {\em if expression} (Line~6) and
{\em if statement} (Line~10) are used to differentiate when a continuation is
created from being called. A continuation is a function (Line~9) if this
continuation has been created but not called, otherwise the continuation is
bound to the value passed by parameter when it is called (\ie~20 in this piece
of code).

If developers need to stop a handler execution, a continuation in the end of the
top-level script should be created. For example, Listing~\ref{lst:rhino_2}:

\begin{lstlisting}[caption=Stopping a \javascript script with continuations., label=lst:rhino_2]
function showMessageHandler() {
  show("This message will be shown");
  stop();
  show("This message will never be shown");
}

var stop = callCC(cont => cont);
\end{lstlisting}

\synccc uses two continuations: the first one stops a handler execution just
after an asynchronous operation invocation, and the second one resumes the
handler execution when the asynchronous operation response is available.
